\begin{thebibliography}{100}


	\bibitem{cdr} DUNE Collaboration. Long-Baseline Neutrino Facility (LBNF) and
		Deep Underground Neutrino Experiment (DUNE) Conceptual Design Report Volume
		2: The Physics Program for DUNE at LBNF. \textit{Fermilab}.
		\href{https://arxiv.org/abs/1512.06148}{\texttt{arXiv:1512.06148}}. 2015.

	\bibitem{ROOT} The ROOT team. ROOT framework for data processing.
		\url{https://root.cern.ch}.

	\bibitem{hyperk} Hyper-Kamiokande proto-collaboration. Hyper-Kamiokande
		Design Report. \href{http://www.hyperk.org/?p=215}{\textit{KEK Preprint.}}
		2016.

	\bibitem{cdr-all} 
	DUNE Collaboration. Long-Baseline Neutrino Facility (LBNF) and
		Deep Underground Neutrino Experiment (DUNE) Conceptual Design Report.
		\href{https://web.fnal.gov/project/LBNF/ReviewsAndAssessments/LBNF_DUNE\%20DOE\%20CD-1\%20Refresh\%20Review/SitePages/Conceptual\%20Design\%20Report.aspx}{\textit{Fermilab}}.



	\bibitem{pauli} Pauli W.
		\href{http://microboone-docdb.fnal.gov/cgi-bin/RetrieveFile?docid=953;filename=pauli\%20letter1930.pdf}{Open letter to the group of radioactive people at the 
Gauverein meeting in Tübingen}. 4 Dec 1930.
	\bibitem{cowan} Cowan C L Jr, Reines F, Harrison F B, Kruse H W, McGuire A D.
		Detection of the Free Neutrino: a Confirmation. \textit{Science,
		\textbf{124}, 3212.} 1956.
	%\bibitem{fermi} Fermi E. Versuch einer Theorie der $\beta$-Strahlen. I.
	%	\textit{Z. Physik}. 1934.
	\bibitem{zuber} Zuber K. Neutrino
		Oscillations. \textit{IOP Publishing}. 2004.
	\bibitem{pontecorvo} Pontecorvo B. Electron and muon neutrinos.
		\textit{Soviet Physics JETP, \bf{10}, 1236}. 1960. Reprinted in
		Cambridge Monographs on Particle Physics, Nuclear Physics, and Cosmology,
		edited by Winter K. \textit{Cambridge University Press}. 1991.
	\bibitem{danby} Danby G, Gaillard J-M, Goulianos K, Lederman L M, Mistry N,
		Schwartz M, Steinberger J. Observation of High-Energy Neutrino Reactions
		and the Existence of Two Kinds of Neutrinos. \textit{Phys. Rev. Letters,
		\bf{9}, 1}. 1962.
	\bibitem{pontecorvo-osc} Pontecorvo B. Neutrino experiments and the problem of
		conservation of leptonic charge. \textit{Soviet Physics JETP, \textbf{26},
		984.} 1968.
	\bibitem{donut} DONUT Collaboration. Observation of Tau Neutrino
		Interactions.
		\href{https://arxiv.org/abs/hep-ex/0012035}{\texttt{arXiv:hep-ex/0012035}}.
		2000.

	\bibitem{smirnov} Smirnov A Yu. Solar neutrinos: Oscillations or
		No-oscillations?
		\href{https://arxiv.org/abs/1609.02386}{\texttt{arXiv:1609.02386}}. 2016.



		

	\bibitem{schwichtenberg} Schwichtenberg J. Physics From Symmetry (2nd Ed.).
		\textit{Springer International Publishing.} 2018.

	\bibitem{superk} The Super-Kamiokande Collaboration. Evidence for oscillation
		of atmospheric neutrinos.
		\href{https://arxiv.org/abs/hep-ex/9807003}{\texttt{arXiv:hep-ex/9807003}}. 1998.

	\bibitem{cohen} Cohen A, Glashow S, Ligeti Z. Disentangling neutrino
		oscillations. \textit{Physics Letters B, \textbf{678}, Issue 2.} 2008.

	\bibitem{langacker} Langacker P. The Standard Model and Beyond (2nd Ed.).
		\textit{CRC Press}. 2017.

	\bibitem{wolfenstein} Wolfenstein L. Neutrino oscillations in matter.
		\textit{Phys. Rev. D \textbf{17}, 2369}. 1978.

	\bibitem{mikheyev-smirnov} Mikheyev S, Smirnov A. Resonance enhancement of
		oscillations in matter and solar neutrino spectroscopy. \textit{Soviet
		Journal of Nuclear Physics \textbf{42:6}.} 1985.

	\bibitem{ricciardi} Ricciardi S. Lecture Notes on Neutrino oscillations in
		matter.
		\url{http://hepwww.rl.ac.uk/ricciardi/Lectures/MSW-1.pdf}. 2013.

	\bibitem{ohlsson} Ohlsson T, Snellman H. Three flavor neutrino oscillations
		in matter.
		\href{https://arxiv.org/abs/hep-ph/9910546v4}{\texttt{arXiv:hep-ph/9910546}}. 1999.

	\bibitem{kneller} Kneller J, McLaughlin G. Three Flavor Neutrino Oscillations
		in Matter: Flavor Diagonal Potentials, the Adiabatic Basis and the CP
		phase. \href{https://arxiv.org/abs/0904.3823}{\texttt{arXiv:0904.3823}}. 2009.

	\bibitem{davis} Davis R Jr, Harmer D, Hoffman K. Search for Neutrinos from
		the Sun. \textit{Phys. Rev. Lett. \textbf{20}, 1205}. 1968.
	\bibitem{sno} SNO Collaboration. Measurement of the Rate of $\nu_e + d
		\rightarrow p + p + e^-$ 
		Interactions Produced by $^8B$ Solar Neutrinos at the Sudbury Neutrino
		Observatory. \textit{Phys. Rev. Lett. \textbf{87}, 071301}. 2001.
	\bibitem{superk-solar} Super-Kamiokande Collaboration. Solar $^8B$ and hep
		Neutrino Measurements from 1258 Days of Super-Kamiokande Data.
		\textit{Phys. Rev. Lett. \textbf{86}, 5651}. 2001.

	\bibitem{kamland} KamLAND Collaboration.  First Results from KamLAND:
		Evidence for Reactor Anti-Neutrino Disappearance. \textit{Phys. Rev. Lett.
		\textbf{90}, 021802}. 2003.

	\bibitem{minos} MINOS Collaboration. Combined Analysis of $\nu_\mu$
		Disappearance and $\nu_\mu\rightarrow \nu_e$ Appearance in MINOS Using
		Accelerator and Atmospheric Neutrinos. \textit{Phys. Rev. Lett.
		\textbf{112}, 191801}. 2014.

	\bibitem{nova} NO$\nu$A Collaboration. Measurement of the Neutrino Mixing
		Angle $\theta_{23}$ in NO$\nu$A. \textit{Phys. Rev. Lett. \textbf{118},
		151802}. 2017.

	\bibitem{t2k} T2K Collaboration. Combined Analysis of Neutrino and
		Antineutrino Oscillations at T2K. \textit{Phys. Rev. Lett.
		\textbf{118}, 151801}. 2017.

	\bibitem{t2k-13} T2K Collaboration. Indication of Electron Neutrino
		Appearance from an Accelerator-Produced Off-Axis Muon Neutrino Beam.
		\textit{Phys. Rev. Lett. \textbf{107}, 041801}. 2011.


	\bibitem{dayabay} Daya Bay Collaboration. Observation of
		Electron-Antineutrino Disappearance at Daya Bay. \textit{Phys. Rev. Lett.
		\textbf{108}, 171803}. 2012.
	\bibitem{reno} RENO Collaboration. Observation of Reactor Electron
		Antineutrinos Disappearance in the RENO Experiment. \textit{Phys. Rev. Lett. \textbf{108},
		191802}. 2012.
	\bibitem{chooz} Double Chooz Collaboration. Indication of Reactor
		$\overline{\nu}_e$ Disappearance in the Double Chooz Experiment.
		\textit{Phys. Rev. Lett. \textbf{108}, 131801}. 2012.

	%\bibitem{gonzalez-garcia} Gonzalez-Garcia M, Maltoni M, Pe$\tilde{\text{n}}$a-Garay C,
	%	Valle J. Global three–neutrino oscillation analysis of
	%	neutrino data.
	%	\href{https://arxiv.org/abs/hep-ph/0009350}{\texttt{arXiv:hep-ph/0009350}}.
	%	2000.

	\bibitem{pdg} Particle Data Group. Review of Neutrino Masses, Mixing and
		Oscillations.
		\url{https://http://pdg.lbl.gov/2017/reviews/rpp2017-rev-neutrino-mixing.pdf}.
		2017.

	%\bibitem{novat23} The NOvA Collaboration. Measurement of the neutrino mixing
	%	angle $\theta_{23}$ in NOvA.
	%	\href{https://arxiv.org/abs/1701.05891}{\texttt{arXiv:1701.05891}}. 2017.
	\bibitem{raut} Raut S. Synergies and complementarities between proposed
		future neutrino projects.
		\href{https://arxiv.org/abs/1712.02096v1}{\texttt{arXiv:1712.02096}}.
		2017.

	\bibitem{thomson} Thomson M. Modern Particle Physics. \textit{Cambridge
		University Press}. 2013.


	\bibitem{blennow} Blennow M, Coloma P, Huber P, Schwetz T. Quantifying the
		sensitivity of oscillation experiments to the neutrino mass hierarchy.
		\href{https://arxiv.org/pdf/1311.1822.pdf}{\texttt{arXiv:1311.1822}}. 2013.

	\bibitem{ciuffoli} Ciuffoli E, Evslin J, Zhang X. Sensitivity to the
		Neutrino Mass Hierarchy.
		\href{https://arxiv.org/abs/1305.5150v4}{\texttt{arXiv:1305.5150}}. 2013.
	\bibitem{qian} Qian X, Tan A, Wang W, Ling JJ, McKeown RD, Zhang C.
		Statistical Evaluation of Experimental Determinations of Neutrino Mass
		Hierarchy.
		\href{https://arxiv.org/abs/1210.3651}{\texttt{arXiv:1210.3651}}. 2012.

	%\bibitem{barger} Barger V, Marfatia D, Whisnant K. Breaking Eight–fold
	%	Degeneracies in Neutrino CP Violation, Mixing, and Mass Hierarchy.
	%	\href{https://arxiv.org/abs/hep-ph/0112119}{\texttt{arXiv:hep-ph/0112119}}.
	%	2001.




	\bibitem{papadimitriou} Papadimitriou V, et al. Design of the LBNF beamline.
		\href{https://arxiv.org/abs/1704.04471}{\texttt{arXiv:1704.04471}}. 2017.

	\bibitem{cdr_vol3} DUNE Collaboration. Long-Baseline Neutrino Facility (LBNF)
		and Deep Underground Neutrino Experiment (DUNE) Conceptual Design Report
		Volume 3: Long-Baseline Neutrino Facility for DUNE. \textit{Fermilab}. 2015.





	\bibitem{Geant4} The \textsc{Geant4} Collaboration.
		\textsc{Geant4} --- a simulation toolkit. \textit{Nuclear Instruments and Methods in
		Physics Research, \textbf{506}, Issue 3.} 2003. 

	% Matter electron density source
	\bibitem{freund} Freund M, Ohlsson T. Matter Enhanced Neutrino Oscillations
		with a Realistic Earth Density Profile.
		\href{https://arxiv.org/abs/hep-ph/9909501}{\texttt{arXiv:hep-ph/9909501}}.
		1999.

	\bibitem{GENIE} Andreopoulos C, et al. The \textsc{GENIE} Neutrino Monte
		Carlo Generator.
		\href{https://arxiv.org/abs/0905.2517}{\texttt{arXiv:0905.2517}}. 2009.



	\bibitem{ballett} Ballett P, King S, Pascoli S, Prouse N, Wang T.
		Sensitivities and synergies of DUNE and T2HK. \href{
		https://arxiv.org/pdf/1612.07275.pdf}{\texttt{arXiv:1612.07275}}. 2016.
	\bibitem{martin-albo} Martin-Albo J. Sensitivity of DUNE to long-baseline
		neutrino oscillation physics.
		\href{https://arxiv.org/abs/1710.08964}{\texttt{arXiv:1710.08964}}. 2017.

	\bibitem{laguna-lbno} LAGUNA-LBNO Collaboration. The LBNO long-baseline
		oscillation sensitivities with two conventional neutrino beams at different
		baselines.
		\href{https://arxiv.org/abs/1412.0804}{\texttt{arXiv:1412.0804}}. 2014.

	\bibitem{masud} Masud M, Mehta P. Non-standard interactions spoiling the CP
		violation sensitivity at DUNE and other long baseline experiments.
		\href{https://arxiv.org/abs/1603.01380}{\texttt{arXiv:1603.01380}}. 2016.

	\bibitem{t2hkk} Hyper-Kamiokande proto-collaboration. Physics Potentials with
		the Second Hyper-Kamiokande Detector in Korea.
		\href{https://arxiv.org/abs/1611.06118}{\texttt{arXiv:1611.06118}}. 2016.
	%\bibitem{MNS} Maki Z, Nakagawa M, Sakata S. Remarks on the Unified Model of
	%	Elementary Particles. \textit{Progress of Theoretical Physics}. 1962.

	%\bibitem{pdg-ckm} Particle Data Group. Review of CP Violation in the Quark Sector.
	%	\url{http://pdg.lbl.gov/2017/reviews/rpp2017-rev-cp-violation.pdf}. 2017

	%\bibitem{LBNE} The LBNE Collaboration. The Long-Baseline Neutrino Experiment:
	%	Exploring Fundamental Symmetries of the Universe.
	%	\textit{Fermilab.}
	%	\href{https://arxiv.org/abs/1307.7335}{\texttt{arXiv:1307.7335}}. 2014.

\end{thebibliography}
