\begin{thebibliography}{100}

\bibitem{fermi} Fermi E. Versuch einer Theorie der $\beta$-Strahlen. I.
		\textit{Z. Physik}. 1934

\bibitem{zuber} Zuber K. Neutrino
		Oscillations. \textit{IOP Publishing}. 2004

\bibitem{pontecorvo} Pontecorvo B. \textit{Sov. J. Phys.} 1960

\bibitem{smirnov} Smirnov A Yu. Solar neutrinos: Oscillations or
		No-oscillations? \texttt{arXiv:1609.02386}. 2016.

\bibitem{superk} The Super-Kamiokande Collaboration. Evidence for oscillation
		of atmospheric neutrinos. \texttt{arXiv:hep-ex/9807003}. 1998.

\bibitem{pdg_ckm} Particle Data Group. Review of CP Violation in the Quark Sector.
		\texttt{http://pdg.lbl.gov/2017/reviews/rpp2017-rev-cp-violation.pdf}. 2017

\bibitem{MNS} Maki Z, Nakagawa M, Sakata S. Remarks on the Unified Model of
		Elementary Particles. \textit{Progress of Theoretical Physics}. 1962

\bibitem{thomson} Thomson M. Modern Particle Physics. \textit{Cambridge
		University Press}. 2013

\bibitem{cdr} DUNE Collaboration. Long-Baseline Neutrino Facility (LBNF) and
		Deep Underground Neutrino Experiment (DUNE) Conceptual Design Report Volume
		2: The Physics Program for DUNE at LBNF. \texttt{arXiv:1512.06148}. 2015

\bibitem{ciuffoli} Ciuffoli E, Evslin J, Zhang X. Sensitivity to the
		Neutrino Mass Hierarchy. \texttt{arXiv:1305.5150v4}. 2013

\bibitem{qian} Qian X, Tan A, Wang W, Ling JJ, McKeown RD, Zhang C.
		Statistical Evaluation of Experimental Determinations of Neutrino Mass
		Hierarchy. \texttt{arXiv:1210.3651}. 2012

\bibitem{martin-albo} Martin-Albo J. Sensitivity of DUNE to long-baseline
		neutrino oscillation physics. \texttt{arXiv:1710.08964}. 2017


\end{thebibliography}

%%%%% CLEAR DOUBLE PAGE!
\newpage{\pagestyle{empty}\cleardoublepage}